Seshadri constants of curve configurations on surfaces

### 2024-03-19 sc-curve-config.tex
Changes by Krishna-19th March (9:00AM)

In this paper, we continue this study by looking at curve arrangements on arbitrary surfaces. We prove some analogues of the results in \cite{JP} for arbitrary surfaces. We work over the field of complex numbers.

@@

The hyperplane section $X \cap V(x_0 - \zeta x_1)$ is the union of the four lines of type $A$ in $\mathcal{L}$ 
given by  
$x_0 = \zeta x_1 \; \text{and} \; x_2 = \beta_j x_3$
for  $1\leq j \leq 4$. Consequently, the sum of these four lines is linearly equivalent to $\mathcal{O}_X(1)$. Similarly, the sum of the four lines 
$x_0 = \alpha_i x_1 \; \text{and} \; x_2 = \zeta x_3$ is linearly equivalent to $\mathcal{O}_X(1)$. Thus we note that the line 
$x_0 = \zeta x_1 \; \text{and} \; x_2 = \zeta x_3$ is in two different sets of 4 lines each so that the sum of lines in each set is linearly equivalent to $\mathcal{O}_X(1)$.
Using a similar argument, one can see that there are 24 sets of 4 lines each such that each line in $\mathcal{L}$ appears in \textit{exactly} two of the sets and the sum of the 4 lines in each set is linearly equivalent to $\mathcal{O}_X(1)$.

@@

Note that each line $l$ in $\mathcal{L}$ has degree 1 in $\mathbb{P}^3$. From the above discussion, for every line $l \in \mathcal{L}$ it is clear that
		\[
		\frac{\mathcal{O}_X(1)\cdot l}{10} %= \frac{(l_{\alpha_i,\beta_1} + l_{\alpha_i,\beta_2} + l_{\alpha_i,\beta_3} + l_{\alpha_i,\beta_4})\cdot  l_{\alpha_i,\beta_j} }{10} 
		= \frac{1}{10}.
		\]

>>>>

In this paper, we continue this study by looking at connected curve arrangements on arbitrary surfaces. We prove some analogues of the results in \cite{JP} for arbitrary surfaces. We work over the field of complex numbers.

@@

The hyperplane section $X \cap V(x_0 - \zeta x_1)$ is the union of the four lines of type $A$ in $\mathcal{L}$ 
given by  
$x_0 = \zeta x_1 \; \text{and} \; x_2 = \beta_j x_3$
for  $1\leq j \leq 4$. Consequently, the sum of these four lines is linearly equivalent to $\mathcal{O}_X(1)$. Similarly, the sum of the four lines 
$x_0 = \alpha_i x_1 \; \text{and} \; x_2 = \zeta x_3$, 
for $1\leq i \leq 4$, 
is linearly equivalent to $\mathcal{O}_X(1)$. Thus we note that the line 
$x_0 = \zeta x_1 \; \text{and} \; x_2 = \zeta x_3$ is in two different sets of 4 lines each so that the sum of lines in each set is linearly equivalent to $\mathcal{O}_X(1)$.
Using a similar argument, one can see that there are 24 sets of 4 lines each such that each line in $\mathcal{L}$ appears in \textit{exactly} two of the sets and the sum of the 4 lines in each set is linearly equivalent to $\mathcal{O}_X(1)$.

@@

  We first show that the Seshadri ratio computed by a line in $\mathcal{L}$ is $\frac{1}{10}$. 
   As mentioned above, every line in $\mathcal{L}$ contains exactly 10 singular points of $\mathcal{L}$. 
   Note that each line $l$ in $\mathcal{L}$ has degree 1 in $\mathbb{P}^3$.
   So for every line $l \in \mathcal{L}$, 
		\[
		\frac{\mathcal{O}_X(1)\cdot l}{ \sum\limits_{p \in\text{Sing}(\mathcal{L})} \text{mult}_{p} \,l} %= \frac{(l_{\alpha_i,\beta_1} + l_{\alpha_i,\beta_2} + l_{\alpha_i,\beta_3} + l_{\alpha_i,\beta_4})\cdot  l_{\alpha_i,\beta_j} }{10} 
		= \frac{1}{10}.
		\]
